Extracting The Power of Dependent Types

### 2021-09-27 paper.tex
Further trimming.
        * Added (back) compressed  paragraph about monads.
        * Got rid of a^2+b^2 example from the intro.
        * Important: Globally reduced spacing for wrapfigures
        * Important: Macro that turns paragraph environment to
          use less spacing (off now).
        * Important: Reduced spacing around agda code blocks.
          Unfortunately in agda.sty for now, maybe one can do this
          in papart.tex.
99% compressed (two lines remain!)
        * Reduced spacing around mathpar
        * redefined \paragraph to \noindentparagraph.

\renewcommand{\paragraph}[1]{\textbf{\textit{#1. }}}

@@

There are two common approaches to language embedding: deep and shallow.
Shallow embeddings define languages in terms of functions and operators
of the host language.  Programs in shallowly-embedded languages are programs
in the host language, so they are immediately run\-nable; types of the embedded
language are types of the host language, so the host typechecker is used for
checking embedded programs.  The downside of this approach is that we cannot
easily get the representation of embedded programs.

@@

To keep presentation as easy as possible to follow, we have
chosen a simple target language to embed --- we use a subset
of PostScript~\citep{postscript1999language}, a stack-based
language used in the corresponding document format.
%
\figref{sqsum} shows an example of a program
written in our embedding and the PostScript code produced by
our extractor.
%
This paper is not concerned with practical application of
the presented embedding, so we consciously keep the setup as minimal as
possible.  It is powerful enough to motivate the use of dependent
types \emph{within} the embedding, and to demonstrate the essence
of the proposed approach.  While we include many patterns found
in bigger languages, we leave the scaling of the approach out
of the scope of the paper referring the interested reader
to~\cite{DBLP:journals/corr/abs-2105-10819} where we work
out such generalisations.

@@

\item We show how to our approach provides easy support for partial
  evaluation by making use of normalisation in the host language. This
  allows us to use functions of the host language as macros, as well
  as automatically apply optimizations through the use of rewrite
  rules (\secref{partial-evaluation}).
\end{itemize}

>>>>

%\renewcommand{\paragraph}[1]{\textbf{\textit{#1. }}}
\setlength{\intextsep}{0pt}
%\AgdaNoSpaceAroundCode{}
\renewcommand\paragraph{\noindentparagraph}

% This trick is taken from here:
% https://tex.stackexchange.com/questions/346444/mathpartir-abovedisplayskip-and-belowdisplayskip-affect-placement-of-side-con

\usepackage{etoolbox}

\newcommand{\zerodisplayskips}{%
  \setlength{\abovedisplayskip}{2pt}%
  \setlength{\belowdisplayskip}{2pt}%
  \setlength{\abovedisplayshortskip}{2pt}%
  \setlength{\belowdisplayshortskip}{2pt}}
\appto{\normalsize}{\zerodisplayskips}
\appto{\small}{\zerodisplayskips}
\appto{\footnotesize}{\zerodisplayskips}

@@

There are two common approaches to language embedding: deep and shallow.
Shallow embeddings define lan\-gua\-ges in terms of functions and operators
of the host language.  Programs in shallowly-embedded languages are programs
in the host language, so they are immediately run\-nable; types of the embedded
language are types of the host language, so the host typechecker is used for
checking embedded programs.  The downside of this approach is that we cannot
easily get the representation of embedded programs.

@@

To keep presentation as easy as possible to follow, we have
chosen a simple target language to embed --- we use a subset
of PostScript~\citep{postscript1999language}, a stack-based
language used in the corresponding document format.
%
%\figref{sqsum} shows an example of a program
%written in our embedding and the PostScript code produced by
%our extractor.
%
This paper is not concerned with practical application of
the presented embedding, so we consciously keep the setup as minimal as
possible.  It is powerful enough to motivate the use of dependent
types \emph{within} the embedding, and to demonstrate the essence
of the proposed approach.  While we include many patterns found
in bigger languages, we leave the scaling of the approach out
of the scope of the paper referring the interested reader
to~\cite{DBLP:journals/corr/abs-2105-10819} where we work
out such generalisations.

@@

\item We show how to our approach provides easy support for partial
  evaluation by making use of normalisation in the host language. This
  allows us to use functions of the host language as macros,
  and optimise prorgams via rewrite rules (\secref{partial-evaluation}).

  %as well
  %as automatically apply optimizations through the use of rewrite
  %rules (\secref{partial-evaluation}).
\end{itemize}
